%\lipsum[3-4]

%Kristin
%Sachs

There are many people that have made this journey possible. I am forever indebted to them for their support, kindness, love, and encouragement. Though I couldn't possibly express my true gratitude to everyone that helped me get to where I am, I would like to extend thanks to the following people:

To Govind Menon, for agreeing to take me as a student three years ago. I have learned a lot and had my mathematical and scientific horizons pushed in directions that I would have never expected. Your guidance made this possible. 

To Basilis Gidas, committee member, intramural soccer captain, and friend. Your broad expertise on everything from probability theory to molecular biology provided a vital perspective. Playing on the applied math intramural football team with you in my six years at Brown helped keep me sane and left me with lasting memories. 

To Miranda Holmes-Cerfon, for serving on my committee. I've enjoyed our conversations and they have changed how I think about much of the mathematics in this work. Your authority on the subject matter helped me identify ways in which it could be improved.

To others in the Division of Applied Mathematics. The environment that the people here have created has fostered my pursuit of mathematical knowledge. I would like to thank Stu Geman, Matt Harrison, and the rest of the Pattern Theory group for many conversations, seminars, and ideas. To Carly Klivans, for our conversations on polytopes and geometry. Thanks to all of my friends in the division and particularly Ely, Erich, Joe, Kelly, and Laura who started graduate school with me six years ago. Also Nat, for buying me coffee today. 

To my family, for their never ending belief. Mom, thank you for instilling my philosophical outlook that was necessary throughout my education. Dad, thanks for exposing me to numbers, math, and engineering from a young age. To my extended group of parents, Cathy, John, Melissa, Steven, Grandparents, Uncles, and Aunts, for always being there for me. To my siblings Chellie, Hannah, and Yolie; I love you all.

Finally, to Stasya, for being my support and partner in life. I could not have persevered in the tough moments without you by my side. This victory is as much yours as it is mine.

